### 2021-04-23 input/conclusion.tex
temp commit

>>>>

How to design distributed system in order to deal with consistency,
availability and partitioning is something our community has been
working on for a long time.  Though important achievements have been
with now building blocks have been proposed to help developers deal
with these concerns, the advent of the Edge and IoT era raises a new
complexity: how can we lock down the trafic only where it is
essential!
